An Approach to Off-line Handwriting Recognition through Segmentation Techniques and Deep Neural Networks

### 2017-12-17 Report/paper.tex
If statement probke

\subsubsection{Contour combination}
The leftover contours are used to to reconstruct the original words from the text.
This is done by combining multiple contours which consist of parts of words belonging to the same word. 
We have created an algorithm that combines word segments. It is uses the overlap between the bounding box of their contours to find possible combinations.

% Hoe heet die parameter? Wat is de waarde van de parameter. Plaats de namen, de waardes en hun uitleg samen, plaats hier geen algoritme/formule tussen. 
We have a parameter for the allowed gap between parts of the same word, and one for the minimal y-axis overlap of both their boundingboxes.

\begin{equation} %TODO:: FIX INDENTATION, Plaats zoiets in algorithmic
    if \\ 
        wordXaxisGap < \\
            averageWordWidth * (1 / (averageCharacterCount * 2) )\\
        and \\
        wordYaxisOverlap > \\
        min(word1.height, word2.height) * requiredYaxisOverlap\\
    then \\
        combineWords
\end{equation}
The optimal parameters we found are $averageCharacterCount=8$ and $requiredYaxisOverlap=1/2$
Given that these conditions are fulfilled, we can combine both contours into one single contour, containing the found word.

>>>>

\begin{algorithm}[tb]
    \caption{Contour combination algorithm}
    \label{alg:overlap}
\begin{algorithmic}
    \STATE {\bfseries Input:} $contour1$, $contour2$
    \STATE $xGap$ = calculateXaxisDistance $contour1$ $contour2$
    \STATE $yOverlap$ = calculateYoverlap $contour1$ $contour2$
    %TODO ::\IF {$xGap < averageWordWidth * (1 / (averageCharacterCount * 2)) $ {\bfseries and} $yOverlap > min(word1.height, word2.height) * requiredYaxisOverlap$}
    \STATE combineContours $contour1$ $contour2$
\end{algorithmic}
The chosen paramters are:
\\
$averageCharacterCount = 8$ 
\\
$requiredYaxisOverlap = 1/2$
\end{algorithm}

\subsubsection{Contour combination}
The leftover contours are used to to reconstruct the original words from the text.
This is done by combining multiple contours which consist of parts of words belonging to the same word. 
We have created an algorithm \ref{alg:overlap} that decides when to combine two word segments into a single word.
